### 2018-10-01 ms.tex
Add TMB integration and empirical bayes details.

We compared three models 1) a full model with prevalence surveys and aggregated incidence data 2) the submodel with only aggregated incidence data and 3) the benchmark submodel with only prevalence point-survey data. 
The models were implemented and fitted using Template Model Builder \cite{TMB} in R \cite{R}

@@

The Gaussian spatial effect $u(s, \rho, \sigma_u)$ has a Mat\'ern covariance function and two hyper parameters: $\rho$, the nominal range (beyond which correlation is $< 0.1$) and $\sigma_u$, the marginal standard deviation.
The first iid random effect, $v_j \sim \operatorname{Norm}(0, \sigma_v)$,  was grouped by polygon, with all pixels and point surveys within polygon $j$ being grouped together.
This random effect modelled both missing covariates and extra-Poisson sampling error. 
The second iid random effect, $w_i \sim \operatorname{Norm}(0, \sigma_w)$, was applied to each point survey.
This effect modelled extra-binomial sampling noise.
As such, this random effect is not included in the predicted uncertainty in the incidence or prevalence layers.
However, it is included in predictions of out-of-sample point surveys.

>>>>

We compared three models 1) a full model with prevalence surveys and aggregated incidence data 2) the submodel with only aggregated incidence data and 3) the benchmark submodel with only prevalence point-survey data. 
The models were implemented and fitted in R \cite{R} using Template Model Builder \cite{TMB} which allows a Laplace approximation of the posterior to be calculated.

@@

The Gaussian spatial effect $u(s, \rho, \sigma_u)$ has a Mat\'ern covariance function and two hyper parameters: $\rho$, the nominal range (beyond which correlation is $< 0.1$) and $\sigma_u$, the marginal standard deviation.
The first iid random effect, $v_j \sim \operatorname{Norm}(0, \sigma_v)$,  was grouped by polygon, with all pixels and point surveys within polygon $j$ being grouped together.
This random effect modelled both missing covariates and extra-Poisson sampling error. 
The second iid random effect, $w_i \sim \operatorname{Norm}(0, \sigma_w)$, was applied to each point survey.
This effect modelled extra-binomial sampling noise.
As such, this random effect is not included in the predicted uncertainty in the incidence or prevalence layers.
However, it is included in predictions of out-of-sample point surveys.
The randoms effects are all integrated out during the TMB model fitting.
The hyperparameters are fitted during model fitting using empirical Bayes.
In this empirical Bayes scheme the hyperparameters are learned from the data but are treated as point estimates rather than the model using the full posterior of the hyperparameters.
